Reviewer Comments

### 2024-10-19 Review.qmd
Adding line numbers to replies

\textcolor[HTML]{007895}{Reply: This is a very helpful comment about the general structure of the manuscript and we tried to address it as much as possible. This included several points. First, we agree that a general section on data is useful for readers. Thus, we added such a section at the beginning of the manuscript. Second, we modified especially the first paragraphs of the "Spatial patterns" (sub-)sections in order to improve the logical flow of the manuscript. Third, we rearranged and modified the "Connectivity" section as well. We removed the "Structural connectivity" sub-section by including the key statements into the general paragraph about connectivity.}

@@

\textcolor[HTML]{007895}{Reply: We added the term "model-driven" as suggested.}

@@

\textcolor[HTML]{007895}{Reply: Indeed, such a table is very helpful. Thus, we removed all paragraphs that only list software from the specific sections and now list all software in a central table (Tab. 1).}

@@

\textcolor[HTML]{007895}{Reply: We agree that landscape metrics can be extracted straightforwardly from raster data, and we are adding this as an advantage related to them.}

@@

\textcolor[HTML]{007895}{Reply: Indeed, we forgot to add a sub-section title which is added now.}

@@

\textcolor[HTML]{007895}{Reply: We replaced "entropy" with "measure".}

@@

\textcolor[HTML]{007895}{Reply: We added a brief definition of edge length in this context.}

@@

\textcolor[HTML]{007895}{Reply: Similar to landscape metrics, also surface metrics are scale-dependent because both are designed to quantify landscape heterogeneity - which is inherently scale-dependent. We added this explanation including an according literature reference.}

@@

\textcolor[HTML]{007895}{Reply: We removed the term "query" from the sentence because we agree that it is a source of confusion. However, we believe that the sentence using only "areas" instead is clear enough for readers to follow.}

@@

\textcolor[HTML]{007895}{Reply: We agree that the whole section was confusing for readers unfamiliar with the topic. Thus, we reworded it to make it easier to follow by removing a lot of the database jargon.}

@@

\textcolor[HTML]{e93c26}{Reply: TODO Thanks for pointing this out. We added it to the figure.}

@@

\textcolor[HTML]{e93c26}{Reply: TODO}

@@

\textcolor[HTML]{007895}{Reply: We added "flow" as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We added "dispersal" as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We added dispersal as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We added the specification that movement also includes dispersal of plants. Furthermore, we believe that this aspect is now also highlighted due to the other suggestions of the reviewer that we implemented in this section. Generally, we added this each time movement is mentioned in the section.}

@@

\textcolor[HTML]{007895}{Reply: We added "disperse" as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We are unsure why the point about edge artifacts was added to the manuscript. Thus, we completely removed it here since we think it adds more confusion than helping the readers.}

@@

\textcolor[HTML]{007895}{Reply: We agree that the original statement about underlying assumptions was unclear and reworded the sentence.}

@@

\textcolor[HTML]{007895}{Reply: We added this specification as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We agree that this statement is true for most if not all methods presented in this manuscript. However, we believe it is also helpful to keep it in this section specifically. However, we added a new short "Data" section at the beginning of the manuscript in which we also highlight importance of input data specifically.}

@@

\textcolor[HTML]{007895}{Reply: Thank you very much for adding this insightful remark about the references. We reworded the sentence to ensure the remarks are reflected in the manuscript.}

@@

\textcolor[HTML]{007895}{Reply: We added that digital twins benefit from the increasing rate of data generation in ecology.}

@@

\textcolor[HTML]{007895}{Reply: We renamed the section as suggested.}

@@

\textcolor[HTML]{007895}{Reply: We reworded the sentence being more specific about the corresponding references.}

@@

\textcolor[HTML]{007895}{Reply: Thank you for pointing out this detail. We added this as another potentail drawback of the method.}

@@

\textcolor[HTML]{007895}{Reply: We reworded the sentence stating that there are differences between solvers and that the optimal solver depends on the specific problem. However, the best solver could potentially not be accessible due to software licenses.}

>>>>

\textcolor[HTML]{007895}{Reply: This is a very helpful comment about the general structure of the manuscript and we tried to address it the best possible. This included several points. First, we agree that a general section on data models is useful for readers. Thus, we added such a section at the beginning of the manuscript (L65 - 92). Second, we modified especially the first paragraphs of most (sub-)sections in the "Spatial patterns" section to improve the logical flow of the manuscript (L93 - 202). Third, we rearranged and modified the "Connectivity" section as well. We removed the "Structural connectivity" sub-section by including the key statements into the general paragraph about connectivity (L207 - 212).}

@@

\textcolor[HTML]{007895}{Reply: We added the term "model-driven" as suggested (L53 - 55).}

@@

\textcolor[HTML]{007895}{Reply: Indeed, such a table is very helpful. Thus, we removed all paragraphs that list software from the specific sections and include all software in a central table (Tab. 1).}

@@

\textcolor[HTML]{007895}{Reply: We agree that landscape metrics can be extracted straightforwardly from raster data, and we are adding this as an advantage related to them (L102 - 104).}

@@

\textcolor[HTML]{007895}{Reply: Indeed, we forgot to add a sub-section title which is added now (L116).}

@@

\textcolor[HTML]{007895}{Reply: We replaced "entropy" with "measure" (L128 - 130).}

@@

\textcolor[HTML]{007895}{Reply: We added a brief definition of edge length in this context (L144 - 146).}

@@

\textcolor[HTML]{007895}{Reply: Similar to landscape metrics, also surface metrics are scale-dependent because both are designed to quantify landscape heterogeneity - which is inherently scale-dependent. We added this explanation including an according literature reference (L172 - 173).}

@@

\textcolor[HTML]{007895}{Reply: We removed the term "query" from the sentence because we agree that it is a source of confusion. However, we believe that the sentence using only "areas" instead is clear enough for readers to follow (L193-201).}

@@

\textcolor[HTML]{007895}{Reply: We agree that the whole section was confusing for readers unfamiliar with the topic. Thus, we reworded it to make it easier to follow by removing a lot of the database jargon (L193-201).}

@@

\textcolor[HTML]{e93c26}{Reply: Thank you for pointing this out. We added it to the figure.}

@@

\textcolor[HTML]{007895}{Reply: The figure caption now includes more details how the different topcis of the figure are interlinked.}

@@

\textcolor[HTML]{007895}{Reply: We added "flow" as suggested (L204 - 205).}

@@

\textcolor[HTML]{007895}{Reply: We added "dispersal" as suggested (L217 - 219).}

@@

\textcolor[HTML]{007895}{Reply: We added dispersal as suggested (L217 - 219).}

@@

\textcolor[HTML]{007895}{Reply: We added the specification that movement also includes dispersal of plants. Furthermore, we believe that this aspect is now also highlighted due to the other suggestions of the reviewer that we implemented in this section. Generally, we added this each time movement is mentioned in the section (L204 - 284).}

@@

\textcolor[HTML]{007895}{Reply: We added "disperse" as suggested (L227 - 230).}

@@

\textcolor[HTML]{007895}{Reply: We are unsure why the point about edge artifacts was added to the manuscript. Thus, we completely removed it here since we think it adds more confusion than helping the readers (L230 - 232).}

@@

\textcolor[HTML]{007895}{Reply: We agree that the original statement about underlying assumptions was unclear and reworded the sentence (L237 - 239).}

@@

\textcolor[HTML]{007895}{Reply: We added this specification as suggested (L263 - 266).}

@@

\textcolor[HTML]{007895}{Reply: We agree that this statement is true for most if not all methods presented in this manuscript. However, we believe it is also helpful to keep it in this section specifically. However, we added a new short "Data" section at the beginning of the manuscript in which we also highlight importance of input data specifically (L86 - 92).}

@@

\textcolor[HTML]{007895}{Reply: Thank you very much for adding this insightful remark about the references. We reworded the sentence to ensure the remarks are reflected in the manuscript (L331 - 334)}

@@

\textcolor[HTML]{007895}{Reply: We added that digital twins benefit from the increasing rate of data generation in ecology (L365 - 367).}

@@

\textcolor[HTML]{007895}{Reply: We renamed the section as suggested (L392).}

@@

\textcolor[HTML]{007895}{Reply: We reworded the sentence being more specific about the corresponding references (L408 - 410).}

@@

\textcolor[HTML]{007895}{Reply: Thank you for pointing out this detail. We added this as another potentail drawback of the method (L418 - 421).}

@@

\textcolor[HTML]{007895}{Reply: We reworded the sentence stating that there are differences between solvers and that the optimal solver depends on the specific problem. However, the best solver could potentially not be accessible due to software licenses (424 - 429).}
